Verifying Demonstrations

### 2017-08-18 properties.tex
Cleans up contents

\mode*
\section{Verification and privacy}

Alice is an activist who organizes a demonstration for some cause.
Her main goal after the protest is to provide verifiable data.
There are several problems:
\begin{frame}
\begin{itemize}
  \item Alice must prove that the data is related to the event, that it is not 
    reused data from previous demonstrations.
  \item Alice must provide data which can be used for the desired verification 
    of the event.
  \item Alice must also consider the privacy of the participating individuals.
\end{itemize}
\end{frame}
Since many of the current techniques are based on photos, we will give an 
example of Alice's problems in that setting.
How can she ensure that photos from a demonstration are authentic?
We can probably recognize the location that the photo is portraying, however, 
this might just as well be a reconstruction or entirely computer generated.
We cannot trust the meta-data of the photo, such as time-stamps of the file, 
because these can easily be manipulated.
So the only thing we can say for sure is that the photo was taken at the latest 
at the time of publication.
Now, if we cannot trust these photos, how can we determine the number of 
participants of a demonstration?
Furthermore, how can Alice protect the privacy of those in the photos?

\subsection{Verification}
\label{Verification}

@@

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item For valid verification we must have immutable storage.
      \item We need to prevent or detect malicious changes.
    \end{itemize}
  \end{remark}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[V\ref{EligibilityVerif} Eligibility]
    \begin{itemize}
      \item Must verify that the proof is not reused from before.
      \item Must verify that each proof belongs to a unique individual (not 
        only Sybil).
    \end{itemize}
  \end{idea}
\end{frame}

@@

\subsection{Privacy}
\label{Privacy}

>>>>

\mode*
\subsection{Verification and privacy}
\label{VerificationAndPrivacy}

Alice is an activist who organizes a demonstration for some cause.
Her main goal after the protest is to provide verifiable data.
There are several problems:
\begin{frame}
\begin{itemize}
  \item Alice must prove that the data is related to the event, that it is not 
    reused data from previous protests.
  \item Alice must provide data which can be used for the desired verification 
    of the event.
  \item Alice must also consider the privacy of the participating individuals.
\end{itemize}
\end{frame}
Since many of the current techniques are based on photos, we will give an 
example of Alice's problems in that setting.
How can she ensure that photos from a demonstration are authentic?
We can probably recognize the location that the photo is portraying, however, 
this might just as well be a reconstruction or entirely computer generated.
We cannot trust the meta-data of the photo, such as time-stamps of the file, 
because these can easily be manipulated.
So the only thing we can say for sure is that the photo was taken at the latest 
at the time of publication.
Now, if we cannot trust these photos, how can we determine the number of 
participants of a demonstration?
Furthermore, how can Alice protect the privacy of those in the photos?

%However, to complicate things further,
%\blockcquote{VenezuelanStateWorkersCalledToParticipate}{%
%  \textins*{m}any of Venezuela’s 2.8 million state workers have reported 
%  getting text messages, phone calls and being required to attend political 
%  rallies during work hours
%}.
%
%\blockcquote{BBConVenezuelaProtestBan}{%
%  Venezuela is banning protests that could "disturb or affect" Sunday's 
%  controversial election for a new constituent assembly.
%}
%
%\blockcquote{BBConVenezuelaProtestBan}{%
%  Prison terms of between five and 10 years could be imposed on those 
%  contravening the ban,
%}
%
%\blockcquote{VenezuelanGovtBansProtesting}{%
%  Venezuelans are planning to defy a government ban on public demonstrations 
%  and risk deadly repression with marches across the country to protest against 
%  a vote Sunday that opposition forces say will mark the end of democracy
%}

\subsubsection{Verification}
\label{Verification}

@@

@@

@@

\subsubsection{Privacy}
\label{Privacy}
